Considering scale in multilayer animal social networks

### 2020-06-21 paper/manuscript.Rmd
make timedefs dates idates

DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')
nobs <- readRDS('../data/derived-data/05-number-of-observations.Rds')
timedefs <- fread('../data/supp-data/timecut-defs.csv')
```

>>>>

DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')
nobs <- readRDS('../data/derived-data/05-number-of-observations.Rds')
timedefs <- fread('../data/supp-data/timecut-defs.csv')
timedefs[, c('mindate', 'maxdate') := .(as.IDate(mindate), as.IDate(maxdate))]
```
